---
title: "John Y. Campbell & John H. Cochrane (1999) Replication"
author: "Bruno Barbosa"
date: "9/28/2019"
output: html_document
---

# Limpeza de variaveis antigas
```{r}
rm(list = ls())
```

# biblioteca utilizadas
```{r, message=F}
library(gmm)
library(readxl)
library(dplyr)
library(ggplot2)
```

# Parameters assumed

```{r}
g = 0.0189;     # Mean consumption growth rate
sigma = 0.015;  # Standard deviation of log consumption growth
rf = 0.0094;    # Log risk-free rate
phi = 0.87;     # Persistence coefficient
gamma = 2;      # Utility curvature

sigmaw = 0.112; # Standard-deviation of dividend growth
rho = 0.2;      # correlation between deltad e deltac

delta = 0.89; # Utility discount factor
```

We choose the subjective discount factor δ to match the risk-free rate with the average real return on Treasury bills.


# Equaçoes
\[\bar{S} = \sigma \sqrt{\frac{\gamma}{1-\phi}}\]

\[ln(S_{\text{max}}) \equiv ln(\bar{S}) +\frac{1}{2} (1 - \bar{S}^2) \]
```{r}
S_bar.func = function(sigma, gamma, phi){
  ret = sigma*(gamma/(1-phi))^0.5
  return(ret)
}

S_max.func = function(S_bar){
  ret = exp(log(S_bar) + 0.5*(1-S_bar^2))
  return(ret)
}

S_bar = S_bar.func(sigma, gamma, phi)
S_max = S_max.func(S_bar)
```


# Lambda function
define as funções de $\lambda(s_t)$ e $dx_{t+1} / {dc_{t+1}}$

\[\lambda(s_{t}) \begin{cases} \frac{1}{\bar{S}} \sqrt{1-2(s_t - \bar{s}_t)} -1 & s_t \le s_{max} \\ 0 & s_t > s_{max} \end{cases}\]

\[ \frac{dx_{t+1}}{dc_{t+1}} =  1 - \frac{\lambda(s_t)}{S_t^{-1} -1} \]
```{r}
lambda = function(S_grid, S_bar, S_max){
  
  # Inicializa um vetor de retorno
  ret = vector(mode = "double", length = length(S_grid))
  
  ret[log(S_grid) <= log(S_max)] = (1/S_bar)*sqrt(1 -2*log(S_grid[log(S_grid) <= log(S_max)]/S_bar))-1
  ret[log(S_grid) > log(S_max)] = 0
  
  return(ret)
}

dX <- function(S_grid, S_bar, S_max) {
  ret =  1 - lambda(S_grid, S_bar, S_max)/((S_grid**(-1))-1)
  return(ret)
}

```

# Graficos
```{r}
# discretização do eixo x
S_grid = seq(from=0, to=S_max*1.05, length.out = 1000)
S_grid = S_grid[S_grid>0]


# cria uma tabela que contem os dados
data = tibble(S_grid = S_grid, lambda = lambda(S_grid, S_bar, S_max), dX = dX(S_grid, S_bar, S_max))

captionText = sprintf("The vertical solid line shows the steady-state surplus consumption ratio S.\nThe dashed vertical line shows the maximum surplus consumption ratio S_max.")

ggplot(data) +
  geom_line(aes(x=S_grid, y=lambda)) +
  geom_vline(xintercept = S_bar, colour = "black") +
  geom_vline(xintercept = S_max, colour = "black", linetype="dotted") +
  labs(title= "Sensitivity function of lambda(s)", # Title
       subtitle="", # Subtitle
       caption=captionText, # Caption
       y="lambda(s)", 
       x='Surplus consumption ration S=(C_X)/C',
       color=NULL)
  
ggplot(data) +
  geom_line(aes(x=S_grid, y=dX)) +
  geom_vline(xintercept = S_bar, colour = "black") +
  geom_vline(xintercept = S_max, colour = "black", linetype="dotted") +
  labs(title="Implied sensitivity of habit x to contemporaneous consumption", # Title
       subtitle="", # Subtitle
       caption=captionText, # Caption
       y='dx\\dc', 
       x='Surplus consumption ration S=(C_X)/C',
       color=NULL)
```


```{r}

# Steady state surplus ratio, log surplus ratio, and maximum log surplus

T1 = 10000
# Use randn to generate T1+1 N(g,sigma) variates
z = g + sigma*rnorm(T1+1);


# Repositories to collect data
ln_s = rep(log(S_bar), T1+1);
beta = rep(0, T1+1);

# Start log(S) at log(Sbar):
# s[] = log(S_bar);

for(t in 1: T1){

  # Given s(t), calculate lambda(s(t)), then s(t+1) and beta(t)
	# ln_s[t] = min(ln_s[t],log(S_max));
	if(ln_s[t] <= log(S_max)) {
    lb = (1/S_bar)*sqrt(1 -2*(ln_s[t] - log(S_bar)))-1
	} else {
	   ln_s[t] = log(S_max)
	  lb = 0
	}
  
	ln_s[t+1] = phi*ln_s[t] + (1-phi)*log(S_bar) + lb*( z[t+1] - g);
	beta[t] = delta*exp(-gamma*((phi-1)*(ln_s[t]-log(S_bar))-lb*g));
};
  
ttt = tibble(A = ln_s, S = exp(ln_s))



ggplot(ttt[round(nrow(ttt)/2,0):nrow(ttt),], aes(x = S)) +
  geom_histogram(aes(y = ..density..), # the histogram will display "density" on its y-axis
                 bins = 30, colour = "blue", fill = "white") +
  geom_vline(xintercept = S_bar, colour = "black") +
  geom_vline(xintercept = S_max, colour = "black", linetype="dotted") +
  geom_density(alpha = .2, fill="#FF6655") #overlay with a transparent (alpha value) density plot

hist(ln_s)
# Discard initial values. Resulting s & beta are same length, and periods
# are matched up.
beta = beta(discard+1:end);
s = s(discard+1:end-1);
end
# Generate figure 1 in paper with [beta,s] = surplus(100,100). Plot beta
# versus 1:100 (panel A) and beta versus s (panel B). [Actually plots
# sorted beta versus sorted s where sort order is smallest s to biggest s.


```